Placeholder

### 2021-02-06 Paper_Histograms.Rmd
Added eating disorder positive diagnosis by sample chunk

```{r Get MDD positive total}

@@

dat.retro_mdd_by_sample <- dat.retro_mdd_by_sample %>% 
  group_by(Sample_plot) %>% 
  summarise(depressive_disorders = n())

@@

```{r Get anxiety positive total}

@@

dat.retro_anxi_by_sample <- dat.retro_anxi_by_sample %>% 
  group_by(Sample_plot) %>% 
  summarise(anxiety_disorders = n())

>>>>

```{r Get MDD positive by sample}

@@

dat.retro_mdd_by_sample <- dat.retro_mdd_by_sample %>% 
  group_by(Sample_plot) %>% 
  summarise("Depressive disorders" = n())

@@

```{r Get anxiety positive by sample}

@@

dat.retro_anxi_by_sample <- dat.retro_anxi_by_sample %>% 
  group_by(Sample_plot) %>% 
  summarise("Anxiety disorders" = n())

```{r Get eating disorder positive by sample}

dat.retro_ED_by_sample <- dat.retro %>%
  group_by(Sample_plot) %>% 
  select(eating_disorders_numeric) %>% 
  filter(eating_disorders_numeric == 1)

dat.retro_ED_by_sample <- dat.retro_ED_by_sample %>% 
  group_by(Sample_plot) %>% 
  summarise("Eating disorders" = n())
